Removing CO Interlopers from [\CII] Surveys With the Three Field Approach

### 2019-03-12 paper/ms.tex
Finish up CO modelling
Add explicit Fisher matrix calculations

\section{CO Measurements} \label{sec:co_measurements}
\subsection{CO Modelling} \label{ssec:co_modelling}
To model the statistical fluctuation and amplitude of the \CO{} intensity maps
we follow \citet{2016ApJ...825..143L}, and briefly summarize the procedure
here. We begin by assuming a Schechter form for the star formation rate
function,
\beq\label{eq:schechter}
\phi(\SFR)\,\text{d}\SFR = \phi_*
\left(\frac{\SFR}{\SFR_*}\right)^{\alpha}\exp{\left[-\frac{\SFR}{\SFR_*}\right]}
\frac{\text{d}\SFR}{\SFR_*}
\eeq
where $\alpha$ is the faint-end slope, $\SFR_*$ is the characteristic
star-formation rate, and $\phi_*$ is the characteristic number density. The
average specific intensity in a line $l$ can be related to the comoving
emissivity by \citep{2011ApJ...741...70L, 2013ApJ...768...15P},
\beq\label{eq:emiss_to_int}
\avg{I_l} = \frac{\epsilon_l}{4\pi \nu_{\text{rest},l}}\frac{c}{H(z)}\text{,}
\eeq
where $\nu_{\text{rest},l}$ is the rest-frame emission frequency and
$\epsilon_l$ is the comoving emissivity, each of line $l$.

>>>>

\section{CO Measurements} \label{sec:co_measurements}
\subsection{CO Modelling} \label{ssec:co_modelling}
To model the statistical fluctuation and amplitude of the \CO{} intensity maps
we follow \citet{2016ApJ...825..143L}, and briefly summarize the procedure
here. We begin by assuming a Schechter form for the star formation rate
function,
\beq\label{eq:schechter}
\phi(\SFR)\,\text{d}\SFR = \phi_*
\left(\frac{\SFR}{\SFR_*}\right)^{\alpha}\exp{\left[-\frac{\SFR}{\SFR_*}\right]}
\frac{\text{d}\SFR}{\SFR_*}
\eeq
where $\alpha$ is the faint-end slope, $\SFR_*$ is the characteristic
star-formation rate, and $\phi_*$ is the characteristic number density. The
average specific intensity in a line $l$ can be related to the comoving
emissivity by \citep{2011ApJ...741...70L, 2013ApJ...768...15P},
\beq\label{eq:emiss_to_int}
\avg{I_l} = \frac{\epsilon_l}{4\pi \nu_{\text{rest},l}}\frac{c}{H(z)}\text{,}
\eeq
where $\nu_{\text{rest},l}$ is the rest-frame emission frequency and
$\epsilon_l$ is the comoving emissivity, each of line $l$. Assuming a linear
luminosity-SFR relation with a constant of proportionality of $L_0^l$, along
with the Schechter form for the SFR function (Equation~\ref{eq:schechter}), it
follows that \citep{2013ApJ...768...15P},
\beq\label{eq:com_emiss}
\epsilon_l = \phi_* L_0^{l}
\frac{\SFR_*}{1\,\Msun\text{yr}^{-1}}\Gamma{(2+\alpha)}\text{.}
\eeq
We adopt the value of $L_0^{\CO}$ for each line transition from
\citet{2010JCAP...11..016V}.

\subsection{Something} \label{ssec:co_}
We now consider the prospects of measuring the \CO{} transition using the
three-field approach for CONCERTO and CCAT-p. First, let us consider the
concrete example of jointly measuring the CO(5-4), CO(4-3), and CO(3-2) lines
in the redshift range $0.6 < z < 0.725$ with CONCERTO. We label each line with
the upper transitional level, e.g. CO(3-2) is referred to as ``3''. The
relevant Fisher matrix is then,
\beq\label{eq:co_fisher}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} 
V_{\text{surv}} \sum_{l} \sum_{m} 
\frac{\partial \hat{P}_l(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_i(k)}{\hat{P}_j(k)}} 
\frac{\partial \hat{P}_m(k)}{\partial B_j}\text{,}
\eeq
where $l$ and $m$ sum over all three cross-spectra. In our specific case where
the partial derivatives are quite simple, we can simplify this expression for
the off-diagonal elements as,
\beq\label{eq:fisher_simple}
F_{i,j} =
\int \frac{\text{d}k\,k^2}{2\pi^2} 
V_{\text{surv}}
\left[
\frac{B_i B_j}{(B_i B_j)^2 + B_{i,\text{tot}}^2B_{j,\text{tot}}^2}
+\sum_{i', j', k'\,\text{perm.}}
\frac{B_{i'} B_k}{B_{i', \text{tot}}^2 B_{j'} B_{k'} + B_{i'} B_i B_j B_k}
\right]\text{,}
\eeq
where the sum on $i', j', k'$ is over all permutations, i.e. over the three
combinations $(i', j', k') = (1, 2, 3), (2, 3, 1), (3, 1, 2)$. Strikingly the
integrand is independent of $k$, and as a result we can further simplify,
resulting in,
\beq\label{eq:fisher_super_simple}
F_{i,j} = 
\tilde{V_k}
\left(
\frac{B_i B_j}{(B_i B_j)^2 + B_{i,\text{tot}}^2B_{j,\text{tot}}^2}
+\sum_{i', j', k'\,\text{perm.}}
\frac{B_{i'} B_k}{B_{i', \text{tot}}^2 B_{j'} B_{k'} + B_{i'} B_i B_j B_k}
\right)\text{,}
\eeq
where,
\beq\label{eq:Vk}
\tilde{V_k} = \frac{k_{\text{max}}^3}{6\pi^2} V_{\text{surv}}\text{.}
\eeq

We can write down the diagonal elements similarly as,
\beq\label{eq:fisher_offdiagonal}
F_{i,i} = \tilde{V_k}
\left(
\frac{B_j^2}{(B_iB_j)^2+B_{i,\text{tot}}^2B_{j,\text{tot}}^2}
+\frac{B_k^2}{(B_iB_k)^2+B_{i,\text{tot}}^2B_{k,\text{tot}}^2}
+\frac{2B_j B_k}{B_{i,\text{tot}}^2B_jB_k + B_i^2B_jB_k}
\right)\text{.}
\eeq
